---
title: "Text Mining Homework"
output:
  html_document:
    toc: true
    toc_float: true
    number_sections: true
    df_print: paged
    css: ../../../styles.css
  pdf_document: default
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, eval = FALSE, fig.align = "center", message = FALSE, warning = FALSE)
```

# MVP

Using the dataset `austen_books()` from the package `janeaustenr`:

```{r}
library(tidyverse)
library(tidytext)
library(ggwordcloud)
library(text2vec)

ja <- janeaustenr::austen_books()
```



1. Find the most common words in both Pride & Prejudice and Sense & Sensibility.

The most common words in both of these books when assessed together is the, to , of, and, and her
```{r}
ja %>% 
  unnest_tokens(word, text) %>% 
  filter(book %in% c("Pride & Prejudice", "Sense & Sensibility")) %>% 
  count(word, sort = T)

ja %>% 
  unnest_tokens(word, text) %>% 
  filter(book %in% c("Pride & Prejudice", "Sense & Sensibility")) %>% 
  group_by(book) %>% 
  count(word, sort = T) 
  
```

2. Find the most common words in both Pride & Prejudice and Sense & Sensibility, not including stop words.

```{r}
pop_words <- ja %>% 
  unnest_tokens(word, text) %>% 
  filter(book %in% c("Pride & Prejudice", "Sense & Sensibility")) %>% 
  group_by(book) %>% 
  count(word, sort = T) %>% 
  anti_join(stop_words, by = "word")
```
All of the most common words without stop words pretty much are names.. which is quite interesting, but makes sense i guess.


3. Find the most common sentiment words in both Pride & Prejudice and Sense & Sensibility.

```{r}
pop_sentiments <- pop_words %>% 
  inner_join(get_sentiments("bing"), by = "word") %>% 
  filter(word != "miss")
```
The most popular sentiment words are happy, love, pleasure, affection and happiness.

```

