---
title: "Weekend Homework - Model Building"
output:
  html_document:
    toc: true
    toc_float: true
    number_sections: true
    df_print: paged
    css: ../../../styles.css
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.align = 'center')
```
```{r}
library(tidyverse)
library(datasets)
library(CodeClanData)
library(carData)
library(modelr)
library(ggfortify)
library(GGally)
```

# MVP

We've looked at a few different ways in which we can build models this week, including how to prepare them properly. This weekend we'll build a multiple linear regression model on a dataset which will need some preparation. The data can be found in the data folder, along with a data dictionary

We want to investigate the avocado dataset, and, in particular, to model the `AveragePrice` of the avocados. Use the tools we've worked with this week in order to prepare your dataset and find appropriate predictors. Once you've built your model use the validation techniques discussed on Wednesday to evaluate it. Feel free to focus either on building an *explanatory* or a *predictive* model, or both if you are feeling energetic!

As part of the MVP we want you not to just run the code but also have a go at **interpreting the results** and write your thinking in comments in your script.

**Hints and tips**

* `region` may lead to many dummy variables. Think carefully about whether to include this variable or not (there is no one 'right' answer to this!)
* Think about whether each variable is *categorical* or *numerical*. If categorical, make sure that the variable is represented as a factor.
* We will not treat this data as a time series, so `Date` will not be needed in your models, but can you extract any useful features out of `Date` before you discard it?
* If you want to build a predictive model, consider using either `leaps` or `glmulti` to help with this.

index
Date: The date of the observation
AveragePrice: the average price of a single avocado
Total Volume: Total number of avocados sold
4046: Total number of avocados with PLU 4046 sold
4225: Total number of avocados with PLU 4225 sold
4770: Total number of avocados with PLU 4770 sold
Total Bags
Small Bags
Large Bags
XLarge Bags
type: conventional or organic
year: the year
region: the city or region of the observation


```{r}

avocado_prices <- read_csv("data/avocado.csv") %>% janitor::clean_names()
glimpse(avocado_prices)
```


```{r}
library(tidyverse)
library(datasets)
library(CodeClanData)
library(carData)
library(modelr)
library(ggfortify)
library(GGally)
library(lubridate)
```

```{r}
avocado_clean <-  avocado_prices %>% 
  select(-x1) %>% 
  mutate(type = as.factor(type),
         region = as.factor(region),
         month = month(date)) %>% 
  select(-date) %>% 
  mutate(month = as.factor(month))


avocado_prices %>% 
  count(year)
```

```{r}
avocado_clean %>% 
  select(average_price, region) %>% 
  ggplot() +
  aes(x  = region, y = average_price) + 
  geom_boxplot() 

#looks like I don't need to include interactions with regions. There's too many points and theyre quite varied for each region anyway.

avocado_clean %>% 
  select(is.numeric) %>% 
  ggpairs()

avocado_clean %>% 
  select(average_price, !is.numeric, -region ) %>% 
  ggpairs()


alias(lm(average_price ~ ., data = avocado_clean))

```

The primary options for the first part of this model are:

* type
* x4046, x4225, x4770
* total_volume

```{r}

# Just having a quick look at potential first iterations of the model


mod1a <- lm(average_price ~ type, data = avocado_clean)
mod1b <- lm(average_price ~ x4225, data = avocado_clean)
mod1c <- lm(average_price ~ x4770, data = avocado_clean)
mod1d <- lm(average_price ~ total_volume, data = avocado_clean)


autoplot(mod1a)
autoplot(mod1b)
autoplot(mod1c)
autoplot(mod1d)


summary(mod1a)
summary(mod1b)
summary(mod1c)
summary(mod1d)


```

Many of these are producing really odd diagnostic plots. Quick investigate here

```{r}
avocado_clean %>% 
  ggplot() +
  aes(x = average_price, y = x4225) +
  geom_point()

avocado_clean %>% 
  ggplot() +
  aes(x = log(average_price), y = log(x4225)) +
  geom_point()
  

mod1e <- lm(log(average_price ~ log(x4225), data = avocado_clean)
plot(mod1e)

# looks like logging the information isnt going to be helpful in this case. First predictor  -> type
```

```{r}
avocado_clean %>% 
  ggplot() +
  aes(x = average_price) + 
  geom_histogram()

# we can see here that the graph is bimodal. What this means is there are two particular effectors. So it also makes sense here to include type, which has two parameters, into the model.

model_1 <- lm(average_price ~ type, data = avocado_clean)


```

```{r}
avocado_residuals <- avocado_clean %>% 
  add_residuals(model_1, var = "resid") %>% 
  select(-type)


avocado_residuals %>% 
  select(is.numeric) %>% 
  ggpairs()
```

Month is looking like the net best predictor to include. Lets take a quick lool

```{r}
mod2a <- lm(average_price ~ type + month, data = avocado_clean)

anova(lm(average_price ~ type, data = avocado_clean), mod2a)

autoplot(mod2a)

# the tail of the normal qq is all that i'm struggling to capture. maybe its about the type relationships

mod2b <- lm(average_price ~ type * month, data = avocado_clean)
autoplot(mod2a)
autoplot(mod2b)

summary(mod2a)
summary(mod2b)

# The interaction seems to make this a little better
```

```{r}
model_2 <- lm(average_price ~ type * month, data = avocado_clean)

avocado_residuals <- avocado_clean %>% 
  add_residuals(model_1, var = "resid") %>% 
  select(-type, -average_price, -month)

avocado_residuals %>% 
  select(is.numeric) %>% 
  ggpairs()


```

Year is also looking great, so I'll add that in where I can.

```{r}
mod3a <- lm(average_price ~ type * month + year, data = avocado_clean)
mod3b <- lm(average_price ~ type * month + total_volume, data = avocado_clean)
summary(mod3a)
summary(mod3b)
summary(model_2)

autoplot(mod3a)
autoplot(mod3b)
autoplot(model_2)

```

```{r}
model_3 <- mod3a

avocado_residuals <- avocado_clean %>% 
  add_residuals(model_3, var = "resid") %>% 
  select(-type, -average_price, -month, -year, -region)

avocado_residuals %>% 
  ggpairs()
```

I'm thinking to use total_volume, x4046 and large_bags as the next part...


```{r}
mod4a <- lm(average_price ~ type * month + year + month * x4046, data = avocado_clean)
mod4b <- lm(average_price ~ type * month + year + type * total_volume, data = avocado_clean)
mod4c <- lm(average_price ~ type * month + year + type * large_bags, data = avocado_clean)

autoplot(mod4a)
autoplot(mod4b)
autoplot(mod4c)
autoplot(model_3)

```

From these diagnosis plots, I've decided to not add any further predictors to my model. The accuracy seems to be decreasing now and a non-linear relationship is emerging.


Other options for a model would predict the behaviours of prices in each region with pca?




```{r}
library(factoextra)


avocado_numeric <- avocado_clean

avocado_pca <- prcomp(avocado_numeric, 
                    center = TRUE, 
                    scale. = TRUE) 

fviz_eig(avocado_pca)


```

```{r}
summary(avocado_pca)
avocado_pca$rotation
```


```{r}
avocado_mapped <- predict(avocado_pca, newdata = test)
```



