---
title: "Clustering homework"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


* You have been provided some customer data from a shopping centre. Do some exploratory analysis on the data. Comment on findings. 
```{r}
library(tidyverse)
library(cluster)
library(factoextra)
library(corrplot)
library(dendextend)
library(CodeClanData)
library(GGally)
shopping <- read_csv("data/mall_customers.csv") %>% janitor::clean_names()
```
```{r}
shopping %>% 
  select(is.numeric) %>% 
  ggpairs()
```
```{r}
shopping %>% 
  ggplot() + 
  aes(x = spending_score_1_100, y = annual_income_k, colour = age) + 
  geom_point()
```

The findings of these plots suggest that the spending score has a really particular relationship with many of the variables. This will be good for the grouping algorithm i think. Age and annual income also behave in an interesting way.

* We are interested in creating a marketing campaign to target customers based on their spending score and annual income. Perform a k-means clustering to find if there are meaningful clusters in the data to target the customers. 

```{r}
shopping %>% 
  ggplot(aes(x = annual_income_k, y = spending_score_1_100)) + 
  geom_point()
# looks like there will be.
```


* Perform k-means clustering and chose a value of k.

```{r}
shopping_k_data <- shopping %>% select(annual_income_k, spending_score_1_100)

fviz_nbclust(shopping_k_data, kmeans, method = "wss", nstart = 25)
fviz_nbclust(shopping_k_data, kmeans, method = "silhouette", nstart = 25)
fviz_nbclust(shopping_k_data, kmeans, method = "gap_stat", nstart = 25)
```
based on this - especially the sillhoette plot, i would chose a k number of 5.

* Visualise the clustering for your chosen value of k.

```{r}
shopping_model <- shopping_k_data %>% 
  kmeans(
    centers = 5,
    nstart = 25)
clustered_shopping <- augment(shopping_model, shopping_k_data) 

clustered_shopping %>% 
  ggplot() +
  aes(x = annual_income_k, y = spending_score_1_100, colour = .cluster) +
  geom_point()
```


* Do you think the clustering seems a good fit for this data?

the clustering seems a great fir for the model in my opinion.

* Comment on the attributes on one or two of the clusters (maybe even give them a label if you like - like in section 4.1 of the 'Segmentation & clustering intro' lesson). 

the clustering essentially moves people into medium spender scores with a medium income, cluster 1, low spending scores with a high income, cluster 2, low income with  low spending score, 3, low income with high score, 4, and high income with high score.






