---
title: "R Notebook"
output: html_notebook
---

Scales - 
Scales give the details of the mapping from the data to the aesthetic qualities.

```{r}
pets <- CodeClanData::pets
```

```{r}
ggplot(pets, mapping = aes(x = age, y = weight, colour = sex)) +
  geom_point() +
  scale_x_continuous(breaks = seq(2, 12, 3), labels = letters[1:4]) +
  scale_y_continuous(breaks = c(5,7,9,11))
  
```


```{r}
ggplot(pets, mapping = aes(x = age, y = weight, colour = sex)) +
  geom_point() +
  scale_x_continuous(breaks = seq(2, 12, 2)) +
  coord_cartesian((xlim = c(0,8)))
                  
  
```



```{r}
ggplot(pets, mapping = aes(x = age, y = weight, colour = sex)) +
  geom_point() +
  scale_y_continuous(limits = c(0, 8)) 
  
```



```{r}
ggplot(pets) +
  aes(x = animal, fill = sex) +
  geom_bar() +
  coord_flip()
```



to introduce labels you can simply use ylab() and xlab()
to make labels more readable with thousands you can put 
scale_y_continuous(labels = scales::percent/comma/blah/???) investigate the scales package and the help file.
showcol(c()) <- to arrange a colourtheme.



```{r}
pets <- add_case(pets, name = 'CamFraz', sex = 'M', weight = 95, age = 24) 
  
ggplot(pets, mapping = aes(x = age, y = weight, colour = sex)) +
  geom_point() +
  scale_y_log10(name = "log(weight)") 




```

London 244
leeds 110
leatherhead
glasgow 150
edinburgh 140


```{r}
library(CodeClanData)
ggplot(total_sales) +
  aes(x = branch, y = sales) +
  geom_col() +
  coord_flip()


ggplot(total_sales) +
  aes(x = reorder(branch, -sales), y = sales) +
  geom_col() +
  coord_flip()
```

```{r}
total_sales %>% 
  mutate(label_text = ifelse(branch == "Leeds", "The Leeds branch has 715k sales", NA)) %>% 
ggplot() +
  aes(x = branch, y = sales, fill = (branch == "Leeds")) +
  geom_col() +
  scale_fill_manual(values = c('grey40', 'red'), guide = "none") +
  geom_text(aes(label = label_text), colour = "red", size = 4, hjust = 0) +
  coord_flip()
```

```{r}
monthly_sales <- CodeClanData::monthly_sales %>%
  mutate(month = factor(month, levels = c("Jan", "Feb", "March", "April"))) %>% 
  group_by(branch, month) %>% 
  mutate(label_colour = ifelse(sales == max(sales), "RED", NA))

head(monthly_sales)

ggplot(monthly_sales) +
  aes(x = branch, y = sales, fill = month) +
  geom_col(position = "dodge") +
  coord_flip()
```

```{r}
min_max <-max(abs(monthly_sales_april$difference_from_jan))
  

ggplot(monthly_sales_april) +
  aes(
    x = reorder(branch, difference_from_jan),
    y = difference_from_jan,
    fill = difference_from_jan > 0
  ) +
  geom_col() +
  ylim(-min_max, min_max) +
    labs(y = "Difference in sales", x = "Branch location", title = "Sales differences between January and April") + 
  scale_fill_manual(values = c("tomato", "seagreen"), name = "", labels = c("decrease", "increase")) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

