---
title: "Homework"
author: "TK"
date: '2022-04-11'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(prob)
library(janitor)
library(tidyverse)
```
A data set detailing the survival or death of passengers and crew members on the RMS Titanic is given in the data folder for this homework - use this data and not the built-in Titanic dataset in R.

Some time after the disaster a journalist wrote that crew members were more likely to have survived the sinking than passengers. This was disputed by a descendant of one of the surviving crew members, who suggested that the opposite was true, i.e. passengers were more likely to have survived than crew.

```{r}
titanic <- read_csv(here::here("data/titanic.csv"))
```

```{r}
titanic %>% 
  filter(class == "engineering crew"|
         class == "victualling crew"|
         class == "deck crew"|
         class == "restaurant staff")
```

Question
Calculate the conditional probabilities prob(survived∣crew)
 and prob(survived∣passenger)
 to settle this dispute.

```{r}
titanic <- titanic %>% 
  mutate(
    survived = case_when(
      survived == "no" ~ FALSE,
      survived == "yes" ~ TRUE
    )
  )


con_pass <- titanic %>% 
    filter(fare > 0) %>% 
  summarise(mean(survived))

con_crew <- titanic %>% 
    filter(fare == 0) %>% 
  summarise(mean(survived))
```
the conditional chance of survival for passengers is 0.3857475, crew members is 0.2370787	. so you were more likely to be a surviving crew passenger than a surviving passenger.

Question 1.
If I roll a six-sided dice once, what is the probability of getting a number less than 5?
i know in my head that this is 4/6, but how do i work this out?
```{r}
rolldie(1) %>% 
  summarise(mean(X1<5))
```

Question 2.
How many outcomes are there in the sample space of an experiment in which we toss three dice?

```{r}
permutations(6, 3, repeats.allowed = TRUE) %>% 
  dim()
```

there would be 216 this is equal to 6^3

Question 3.
In an experiment where we roll four dice:

how many outcomes are in the event where the total of the four dice equals 5, 6 or 7?

```{r}
rolldie(4) %>% 
  filter(rowSums(.) %in% c(5, 6, 7))
```
there would be 34

what is the probability of this event?

off the top of my head, 34/6^4, so pretty small - 0.026
```{r}
34/(nrow(rolldie(4)))
```

what assumptions do we apply in answering part ii?

we assume that we are counting permutations, not combinations.... right?

Question 4.
Five chairs are placed in a row in a room, along with five people of differing height. The people sit down randomly on the chairs. What is the probability that they sit in order of decreasing height, left to right?

the probability would be 1/5*1/4*1/3*1/2*1 or 1/5! it can either be left to right or right to left so then another 50% chance too. 0.004166667
```{r}
1/(2*factorial(5))
  
```
Question 5.
I roll six dice:

what is the probability I see the numbers 6, 5, 4, 3, 2 and 1 in order on the dice, left to right?

im thinking (1/6)^6 then /2 for the l to r. theres only one permutation of this. 
```{r}
rolldie(6) %>% 
  dim() #dim = 46656 

1/46656 # = 2.143347e-05
2.143347e-05/2 # = 1.071673e-05 rounding error? vv below vv

((1/6)^6)
```


what is the probability I see one each of the numbers 6, 5, 4, 3, 2 and 1 on the dice regardless of order?

```{r}
permutations(6,6) %>% 
dim() 

```

```{r}
720/46656
```
0.0154321

or 

```{r}
(nrow(permutations(6,6)))/(nrow(rolldie(6)))
```

Question 6.
If I draw a single card from a 52-card deck, and it is black, what is the probability that its suit is spades? 

half of cards are black. so first it's out of 26.
next 1/4 of all cards are spades, but only half of all black cards are spades....
so its 50%.

