---
title: "Homework - features and elements of multiple regression"
output:
  html_document:
    toc: true
    toc_float: true
    number_sections: true
    df_print: paged
    css: ../../../styles.css
  pdf_document: default
---

```{r setup, include=FALSE}
library(tidyverse)
knitr::opts_chunk$set(echo = TRUE, fig.align = 'center')
```

<hr>

# MVP

<br>

1. 
```{r}
housing <- read_csv("data/housing_prices.csv")

glimpse(housing)
summary(housing)
```



<br>

2. We expect the `total_rooms` of houses to be strongly correlated with `total_bedrooms`. Use `ggpairs()` to investigate correlations between these two variables.

```{r}
data(housing)
ggpairs(data = housing, columns = 4:5)
```


<br> 

3. So, we do find significant correlations. Let's drop `total_bedrooms` from the dataset, and use only `total_rooms` going forward.

```{r}
housing <- housing %>% select(-total_bedrooms)
```


<br>

4. We are interested in developing a regression model for the `median_house_value` of a house in terms of the possible predictor variables in the dataset. 



  i. Use `ggpairs()` to investigate correlations between `median_house_value` and the predictors (this may take a while to run, don't worry, make coffee or something).
  
  possible predictors -> housing_median_age, total_rooms, population, households, median_income
  
```{r}
housing_matrix <- ggpairs(data = housing, columns = 3:8)
```
  

  ii. Perform further `ggplot` visualisations of any significant correlations you find.
  
```{r}
housing %>% 
  ggplot(aes(x = median_income, y = median_house_value)) +
  geom_point(size = 1, alpha = 0.1) 
```
generally speaking, if a household has a higher income, their house value is much higher.

```{r}
housing %>% 
  ggplot(aes(x = total_rooms, y = median_house_value)) +
  geom_point(size = 0.1)
```
  
```{r}
housing %>% 
  ggplot(aes(x = households, y = median_house_value)) +
  geom_point(size = 0.1)
```
households and total rooms both have a strong relationship with eachother so these plots look similar.
<br>

5. Shortly we may try a regression model to fit the categorical predictor `ocean_proximity`. Investigate the level of `ocean_proximity` predictors. How many dummy variables do you expect to get from it?

```{r}
housing %>% 
  count(ocean_proximity)
```

  there should be 5 levels of predictors.
<br>
 
6. Start with simple linear regression. Regress `median_house_value` on `median_income` and check the regression diagnostics.

```{r}
library(ggfortify)
library(fastDummies)

model <- lm(median_house_value ~ median_income, data = housing) 
summary(model)
```
the regression diagnostics suggest a significant relationship


<br> 

7. Add another predictor of your choice. Check your assumptions, diagnostics, and interpret the model.

```{r}
model2 <- lm(median_house_value ~ median_income:ocean_proximity, data = housing)
plot(model2)
summary(model2) 

```
the model suggests that the relationship between house value and income has the steepest gradient  for islands by far. those near bays and oceans also have a steeper gradient than others, suggesting the ocean is a large factor in house value and income.

# Extension
    
<br>

8. Try adding an interaction between `log(medium_income)` and your chosen categorical predictor. Do you think this interaction term is statistically justified?
```{r}
model3 <- lm(log(median_house_value) ~ log(median_income):ocean_proximity, data = housing)
autoplot(model3)
summary(model3)
```


<br>

9. Find and plot an appropriate visualisation to show the effect of this interaction



